%Input preamble
\input{preamble}

\begin{document}


\title{\Large \textbf{The Effect of Pension Reform on Labor Force Participation in China}}
\author{Yi Ling}

\date{\today}

\maketitle

\thispagestyle{empty} 
\doublespacing
\thispagestyle{empty} 

\section{Research Question}

China faces an aging population, which impacts labor force participation. Therefore, many social security policies, including child allowance, pension policy, aim at extending people's labor supply and mitigating the stress from an aging society. One of the policies is the New Rural Pension Scheme (NRPS) launched in 2009, people in rural areas can receive a monthly subsidy from the government after 60 years old. Under this policy, I want to evaluate the impact of the NRPS on labor supply decisions in rural China. I want to discuss: Does the introduction of the New Rural Pension Scheme in China affect labor supply decisions, particularly in terms of labor market exit among older workers and labor supply adjustments among younger cohorts?

While previous evidence on China's pension reform focuses on pension wealth and household savings, few studies evaluate the impacts on labour force participation. The study most closely related to this idea is \cite{huaDoesPensionAffect2022}, who found the insignificant impact of pension reform on working hours, migration. However, since pension reform has a long-term impact on household behaviours, this paper does not fully capture the effects on the duration of labor force participation. \citet{fengPublicPensionHousehold2011a} also find that the pension reform leads to an increase in household savings from the 1999 urban household pension reform. This idea is inspired by the macroeconomic evidence from \citet{biPublicPensionReforms2023}, which analyzes the effect of pension retrenchment on labor participation with implementation lags across different OECD countries, they found that, people who are close to retirement age will exit the market, while others who get the news about pension retrenchment will choose to work longer. 


\section{Economic Framework and Empirical Design}
To discuss the impact of pension reform on the market exit of people who are close to retirement age, I plan to conduct a Regression Discontinuity regression. Since people who are older than 60 can receive the subsidy, I plan to set up the age range between 50 to 70, to see whether the access to pension benefits leads to earlier labor market exit among those just above the age cutoff compared to those just below it. To evaluate the impact of pension reform on the working hours of young people (age from 20 to 50) from rural areas, by setting up a Difference-in-Difference model, I aim to identify whether the expectation of receiving future pension benefits increases current working hours.

\section{Data}
China Family Panel Studies (CFPS) provides detailed information about employment decisions, wealth, and income status at all ages. With comprehensive data from 25 provinces, the dataset could represent the economic status and well-being of Chinese households from the perspective of economic activities, education, which can identify whether the household can receive the pension and their working status over years.

\bibliography{references}

\end{document}

